### 2021-04-28 yfcc100m/paper/vldb2021/design.tex
Change font of API snippets

\begin{listing}[ht!]
\begin{minted}[frame=single,
              framesep=3mm,
              linenos=true,
              xleftmargin=21pt,
              tabsize=4]{js}
"AddEntity"{
    "_ref" : 1,
    "class": "autotag",
    "properties": {
        "name": "alligator"
    }
},
"AddImage":{
    "_ref": 2,
    "properties": {
        "latitude":  36.23433,
        "longitude": -116.80666
    },
    "format": "jpg"
}
"AddConnection": {
    "ref1": 1,
    "ref2": 2,
    "properties": {
        "prob": 0.7653
    }
}

@@

\begin{listing}[ht!]
\begin{minted}[frame=single,
              framesep=3mm,
              linenos=true,
              xleftmargin=21pt,
              tabsize=4]{js}
"FindEntity"{
    "class": "autotag",
    "constraints": {
        "name": ["==", "alligator"]
    }
    "_ref" : 1
},
"FindImage":{
    "format": "png",
    "constraints": {
        "latitude": [">=", 36.23433,
                     "<=", 38.23433]
        "longitude":[">=", -114.80666,
                     "<=", -116.80666]
    },
    "operations": [{
            "type": "resize",
            "height": 224,
            "width":  224,
        }, {
            "type": "rotate",
            "angle": 45.34
    }],
    "link": {
        "ref":1,
        "constraints": {
            "prob": [">=", 0.66]
        }
    }
}

>>>>

\begin{listing}[ht!]
\begin{minted}[frame=single,
              framesep=3mm,
              linenos=true,
              xleftmargin=21pt,
              fontsize=\footnotesize,
              tabsize=4]{js}
"AddEntity"{
    "_ref" : 1,
    "class": "autotag",
    "properties": {
        "name": "alligator"
    }
},
"AddImage":{
    "_ref": 2,
    "properties": {
        "latitude":    36.23433,
        "longitude": -116.80666
    },
    "format": "jpg"
},
"AddConnection": {
    "ref1": 1,
    "ref2": 2,
    "properties": {
        "prob": 0.7653
    }
}

@@

\begin{listing}[ht!]
\begin{minted}[frame=single,
              framesep=3mm,
              linenos=true,
              xleftmargin=21pt,
              fontsize=\footnotesize,
              tabsize=4]{js}
"FindEntity"{
    "_ref" : 1,
    "class": "autotag",
    "constraints": {
        "name": ["==", "alligator"]
    }
},
"FindImage":{
    "format": "png",
    "constraints": {
        "latitude": [">=", 36.23433,
                     "<=", 38.23433]
        "longitude":[">=", -114.80666,
                     "<=", -116.80666]
    },
    "operations": [{
            "type": "resize",
            "height": 224,
            "width":  224,
        }, {
            "type": "rotate",
            "angle": 45.34
    }],
    "link": {
        "ref":1,
        "constraints": {
            "prob": [">=", 0.66]
        }
    }
}

### 2021-04-28 yfcc100m/paper/vldb2021/eval.tex
Add resize comparison plot to eval
Move figures around to make them fit better
Change font of API snippets

@@

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{figures/plot_th_16_mosaic_results_throughput}
\caption{Throughput Analysis using all queries from our use-case
described in the Experimental Setup Section.
We show queries in different figures for readability reasons.
The experiments show the performance of all systems (VDMS and the two baselines) as the
database size increases.
These queries were run using 16 simultaneous clients (nthr = 16),
and averaged out of 5 runs.}
\label{fig:q_throughput_16}
\end{figure}

>>>>

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{figures/plot_th_16_mosaic_results_throughput}
\caption{Throughput Analysis using all queries from our use-case
described in the Experimental Setup Section.
We show queries in different figures for readability reasons.
The experiments show the performance of all systems (VDMS and the two baselines) as the
database size increases.
These queries were run using 16 simultaneous clients, and averaged out of 10 runs.}
\label{fig:q_throughput_16}
\end{figure}

%% ========= Resize Comparison

\begin{figure}[h!]
% WAS: begin{figure*}[ht]; textwidth
\includegraphics[width=\columnwidth]{figures/plot_th_56_mosaic_results_throughput_resize}
\caption{Throughput Analysis using a subset of the queries, with and without resize.}
\label{fig:q_throughput_56_resize}
\end{figure}

@@
